Pretty darn good control: when are approximate solutions better than approximate models

### 2023-06-26 manuscript/manuscript.Rmd
mini

The state space used was normalized case-by-case as follows: 
*1)* for the single species model, a line segment $[0,1]$, *2)* for all three-species models, a cute $[0,1]^{\times 3}$.
We used simulation data to derive a bound on the population sizes typically observed, and thus be able to normalize states to a finite volume.

>>>>

The state space used was normalized case-by-case as follows: 
*1)* for the single species model, a line segment $[0,1]$, *2)* for all three-species models, a cube $[0,1]^{\times 3}$.
We used simulation data to derive a bound on the population sizes typically observed, and thus be able to normalize states to a finite volume.
